Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Validation

### 2012-12-05 paper.tex
new ref

The presence of $q_i$ in this expression serves as a reference state.
The idea is that the error in the characteristic projection of the
jump (due to the nonlinearity) is minimized if we pick a suitable
reference state, since we only care about the jumps carried to the
interface over the timestep.  The original Castro implementation used
the cell-average quantity.  Experiments found that this is ill-behaved
in the presence of strong shocks (especially at low resolution). For
the present work, we switch the reference state to the jump carried by the 
fastest wave moving toward the interface, $\mathcal{I}_+(\sigma_3)$ in this
case, where the $3$ here means the wave associated with the $u + c$ eigenvalue.
This is in agreement with \citet{ppmunsplit} (eq. 90).  This makes our
expression appear as:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = \mathcal{I}_+(\sigma_3) -
   \sum_{\nu;\lambda^{(\nu)}\ge 0} l^{(\nu)} \cdot \left [
        \mathcal{I}_+(\sigma_3)  - \mathcal{I}_+(\sigma_\nu)
       \right ] r^{(\nu)}
\end{equation}

>>>>

The presence of $q_i$ in this expression serves as a reference state.
The idea is that the error in the characteristic projection of the
jump (due to the nonlinearity) is minimized if we pick a suitable
reference state, since we only care about the jumps carried to the
interface over the timestep \citep{colellaglaz1985}.  The original
Castro implementation used the cell-average quantity.  Experiments
found that this is ill-behaved in the presence of strong shocks
(especially at low resolution). For the present work, we switch the
reference state to the jump carried by the fastest wave moving toward
the interface, $\mathcal{I}_+(\sigma_3)$ in this case, where the $3$
here means the wave associated with the $u + c$ eigenvalue.  This is
in agreement with \citet{ppmunsplit} (eq. 90).  This makes our
expression appear as:
\begin{equation}
q_{i+1/2,L}^{n+1/2} = \mathcal{I}_+(\sigma_3) -
   \sum_{\nu;\lambda^{(\nu)}\ge 0} l^{(\nu)} \cdot \left [
        \mathcal{I}_+(\sigma_3)  - \mathcal{I}_+(\sigma_\nu)
       \right ] r^{(\nu)}
\end{equation}
